% original author: Jeremy Kun
\documentclass[11pt]{moderncv}
\moderncvtheme[blue]{classic}
\usepackage[utf8]{inputenc}
\usepackage{color}

% title metadata
\firstname{Jeffrey}
\familyname{Cordova}
\title{(702)595-6601} 
\email{jeffdcor@gmail.com}

\definecolor{MidnightBlue}{rgb}{0.1, .35, .65}

\begin{document}
	\maketitle
	\section{Education}
		\cventry{2015 - Present}
				{B.S. Student in Mathematical Sciences}
				{University of Nevada, Las Vegas, Department of Mathematical Sciences}
				{Las Vegas}{NV}
				{Interests include statistics, computer science, and economics.}  
		\cventry{2007 - 2015}
				{A.S. Student in Mathematics}
				{College of Southern Nevada}
				{Las Vegas}{NV}
				{}
		\cventry{2006 - 2007}
				{B.S. Student in Civil Engineering}
				{University of Nevada, Reno, Department of Engineering}
				{Reno}{NV}
				{}
	\section{Experience}
		\cventry{Aug. 2013 - June 2014}
				{CLT Representative}
				{Zappos.com}
				{Las Vegas}{NV}
				{Assisted customers with any and all inquiries through multiple contact channels, such as phones, email, and live chat.  In addition to main job duties, worked on a team that updated and maintained an informational system for employees.}
		\cventry{July 2012 - Sep. 2012}
				{Zipline Operations Manager}
				{Buffalo Chip}
				{Sturgis}{SD}
				{Oversaw the construction and operation of three professionally-engineered ziplines at the 2012 Sturgis Motorcycle Rally and the Central States Fair.}
		\cventry{Feb. 2011 - Apr. 2012}
				{Operations Supervisor}
				{Fremont Street Flightlinez}
				{Las Vegas}{NV}
				{Oversaw operations of one of the highest-volume ziplines in the world, encompassing 60+ employees and serving an average of 1,200 customers per day.  Applied the principles of data analysis and process optimization to improve the efficiency of operation procedures, leading to an increase in revenue.  Utilized reporting and visualization software to transform data into valuable insights for management and ownership.}
		\cventry{May 2010 - Oct. 2010}
				{Lifeguard}
				{The Bellagio Hotel}
				{Las Vegas}{NV}
				{Maintained a safe environment, acted as the first response in emergencies, and assisted guests with services and information.}
		\cventry{Sep. 2007 - Sep. 2008}
				{Front Desk Representative}
				{24-Hour Fitness}
				{Henderson}{NV}
				{Occupied the front desk of a fitness gym and pool complex, operated a cash register for membership and product transactions, and used a computer system to assist customers with membership issues and any other inquiries.}

	\section{Technical Skills}
		\cvline{Languages}{Python, R, SQL, Julia, Javascript}
		\cvline{Operating Systems}{Windows (Vista/7/8/10), OS X, Linux (Arch, Ubuntu, Mint)}
		\cvline{Design}{HTML, CSS, TeX}
		\cvline{Office Tools}{Microsoft Word, Excel, PowerPoint, Outlook}
		\cvline{Databases}{MySQL}

\end{document}